An Improvement of Controlling Quality of \\Large Scale Water-Level Data in Thailand

### 2015-04-02 paper.tex
edit introduction

\begin{abstract}
%\boldmath
Extremely change in precipitation level such as water level can cause severe damage. In order to acknowledge changes, Hydro and Agro Informatics Institute has installed telemetry system across Thailand to collect and analyze precipitation level. However, to use its data in researching, incorrect data must be filtered. In previous work, we successfully detect various problems in water level data accurately. Still, outliers detection algorithm  and missing pattern proposed in the previous work still room for improvement in terms of running time and ease of implementation. In this paper, we propose to improve the clustering algorithm in the previous work ...

Still, outliers algorithm proposed in the previous work has  run-time complexity from $O(n\log{n})$ up to $O(n^2)$, which are not quite suitable for large-scale data. Missing pattern algorithm has $O(n\log{n})$ complexity but it use complicated data structure. In this paper, we aim to improve these algorithms. As a result, we can speed up the outlier algorithm to $O(n)$ and hold the missing pattern's complexity at $O(n \log{n})$ but with simpler algorithm. Moreover, compared with the previous work, we measure actual running time of our algorithms and found that they significantly help reduce the running time {\color{red} remove math symbol from abstract.}.

@@

In order to conduct researches, they have collected precipitation data by installing telemetry systems across Thailand. The telemetry system is a device that is used to collect physical, chemical, and biological data from its various sensors [3]. For instance, river’s water level, rainfall level, humidity, and temperature can be measured. Today, HAII have already installed over 800 telemetry systems. The data collected from the telemetry systems is sent back to HAII’s server by using GPRS cellular network [4].

@@

To filtered out incorrect data efficiently, our previous work [5] proposed algorithms to detect anomalies in water level data, which includes outliers, inhomogeneity, and missing pattern algorithm. Example of anomaly data detected by these algorithms is illustrated in figure \ref{fig:example_outliers}, figure \ref{fig:example_inhomogeneity}, and figure \ref{fig:example_missingpattern}. {\color{red} However, when we implement this algorithm to use with real precipitation level data, a problem arise. Since HAII use `R` as a main programming languages for all data analytic tasks, implementing outliers and missing pattern algorithm may leads to $O(n^2)$ in complexity. This inefficiency is originated from two main points. First, The bottleneck of both algorithms is occurred from clustering algorithm. The previous work use \textit{DBSCAN} [6] as the clustering algorithm which have $O(n^2)$ complexity if it is a naive implementation and $O(n\log{n})$ if it is implemented using special data structures that support fast region query such as \textit{R*-Tree} or \textit{k-d Tree} , which seem to be much more complex. Second, Our last work is implemented in HAII using \texttt{R} library called \texttt{fpc} which contains \textit{DBSCAN} library that have $O(n^2)$ complexity [7]. Thus, the overall algorithms’ complexity become $O(n^2)$.}

@@

{\color{blue}
	New Paragraph Here

	However, when we implement this algorithm to use with real precipitation level, we have found some interesting facts. According to the previous paper, both outliers detection algorithm and missing pattern algorithm depend on \textit{DBSCAN} [6] as the clustering algorithm. For outliers algorithm, \textit{DBSCAN} have $O(n^2)$ complexity if it is a naive implementation and $O(n\log{n})$ if it is implemented using special data structures that support fast region query such as \textit{R*-Tree} or \textit{k-d Tree} , which seem to be much more complex. 
}

@@

\begin{figure}
	\includegraphics[width=\linewidth]{figure2.png}
	\caption{Example of data with inhomogeneity.}
	\label{fig:example_inhomogeneity}
\end{figure}

@@

{\color{red}
This paper proposes an improvement in outliers and missing pattern algorithms for large-scale water level data. Our main goal is to refine both algorithms to be simple, yet expeditious, while bring out the same results as our previous work. We have reduce running time of outliers algorithm from $O(n^2)$ or $O(n \log{n})$, depends on data structures, to $O(n)$. Also, missing pattern is decresed from $O(n^2)$ or $O(n \log^2{n})$ to $O(n \log{n})$. This can be  done by imitating the clustering result with more simple and fast approach which we will discuss later. The experimental result revealed that our approach significantly cuts down the overall running time in large-scale data.
}

@@

Currently, Hydro and Agro Informatics Institute (HAII) have already installed over 800 telemetry system across Thailand. \textbf{\color{red}Add Map Figure!}Figure 4 shows example of location where telemetry systems were installed. Each system send data from its many sensors back to central database every 10 minutes via cellular network. From these numbers, we can estimate that there are 3.45 million records of data added to database every month. Since HAII have collected precipitation data for over 5 years, we can assume that we are dealing with approximately 207 million records. In previous paper, we use water level data for both outliers and missing pattern algorithms. Moreover, because of the nature of water level in the river, water level's value should be continuous without sudden change. Moreover, data is stored in timestamp order.

>>>>

\begin{abstract}
%\boldmath
Extremely change in precipitation level such as water level can cause severe damage. In order to acknowledge changes, Hydro and Agro Informatics Institute has installed telemetry system across Thailand to collect and analyze precipitation level. However, to use its data in researching, incorrect data must be filtered. In previous work, we successfully detect various problems in water level data accurately. Still, outliers detection algorithm  and missing pattern algorithm proposed in the previous work still room for improvement in terms of running time and ease of implementation. One of problems is that both algorithms is relied on complicated clustering which is unnecessary. In this paper, we propose to improve the clustering algorithm used in the previous work for water-level data. A linear clustering algorithm is invented and used to replace the old clustering algorithm. As a result, we can speed up the outliers detection algorithm and hold the same running time on missing pattern algorithm but increase simplicity and ease of implementation. Moreover, compared with the previous work we measure actual running time of our algorithms and found that they significantly help reduce the running time.

@@

In order to conduct researches, they have collected precipitation data by installing telemetry systems across Thailand. The telemetry system is a device that is used to collect physical, chemical, and biological data from its various sensors [3]. For instance, river’s water level, rainfall level, humidity, and temperature can be measured. Currently, Hydro and Agro Informatics Institute (HAII) have already installed over 800 telemetry system across Thailand. \textbf{\color{red}Add Map Figure!}Fig. 3 shows example of location where telemetry systems were installed. Each system send data from its many sensors back to central database every 10 minutes via cellular network. And, all of the data is stored order by timestamp. From these numbers, we can estimate that there are 3.45 million records of data added to database every month. Since HAII have collected precipitation data for over 5 years, we can assume that we are dealing with approximately 207 million records.

@@

To filtered out incorrect data efficiently, our previous work [5] proposed algorithms to detect anomalies in water level data, which includes outliers, and missing pattern algorithm. Example of anomaly data detected by these algorithms is illustrated in Fig. \ref{fig:example_outliers}, and Fig. \ref{fig:example_missingpattern}. However, both outliers detection algorithms and missing pattern is heavily relied on clustering algorithm. \textit{DBSCAN} algorithm is used to do the clustering task. The \textit{DBSCAN} itself have $O(n\log{n})$ running time if it is implemented using special data structures that support region query such as \textit{R*-Tree} or \textit{k-d Tree}, which seem to be very complex, and it have $O(n^2)$ running time if no special data is used. This can cause outlier detection algorithm's running time rise up to $O(n\log{n})$ or $O(n^2)$, which is not quite suitable for over 200 million records of data. Moreover it unnecessarily add complication and time used in implementing both algorithms. Also, real runtime might be slow due to overhead of the algorithms.

@@

In this paper, we proposed to improve the clustering algorithm in the previous work for water-level data. A linear clustering algorithm is invented and used to replace \textit{DBSCAN} clustering. The linear clustering algorithm helps improve both outliers detection algorithm and missing pattern algorithm for water-level data. As a result, the linear clustering algorithm helps increase speed and simplicity, yet maintain same accuracy of the algorithms. The outliers detection algorithm's running time is dwindled to $O(n)$. The missing pattern algorithm also achieves faster real running-time, even though holds the same theoretical running-time as previous work at $O(n log{n})$.

@@

@@

@@

Currently, Hydro and Agro Informatics Institute (HAII) have already installed over 800 telemetry system across Thailand. \textbf{\color{red}Add Map Figure!}Fig. 3 shows example of location where telemetry systems were installed. Each system send data from its many sensors back to central database every 10 minutes via cellular network. From these numbers, we can estimate that there are 3.45 million records of data added to database every month. Since HAII have collected precipitation data for over 5 years, we can assume that we are dealing with approximately 207 million records. In previous paper, we use water level data for both outliers and missing pattern algorithms. Moreover, because of the nature of water level in the river, water level's value should be continuous without sudden change. Moreover, data is stored in timestamp order.
